A large-scale study of polymorphism in R

### 2019-03-16 paper/main.tex
working on biblio, and added small paper things

%
%
%
\section{Background}

%
%
%
%
\subsection{The R Programming Language}

@@

%
%
\subsection{The \texttt{genthat} Package}

@@

\AT{We use/modify the {\tt genthat} tracer, probably worth going in to more detail here.}

%
%
%
%
%
%
\section{Motivation and High-level Overview}

R is a languages written by and for \textit{statisticians}.  It traces its
roots to the S language, developed by ... .  R programmers don't write big
servers or software systems; instead, they write and modify small data
processing pipelines as a means to facilitate interaction with digital data.
This leads to ``front-line'' R code (i.e., code written for users, not
programmers) not being made available on typical platforms like Github.
\AT{Maybe front-line code isn't a good word, is there a good way to describe
  non-library code?}  Put differently, R is essentially a really big
domain-specific language.

%
%
%
%
%
%
\section{The Method}

@@

>>>>

R is a languages written by and for \textit{statisticians}.  It traces its
roots to the S language~\cite{becker1988new}, developed by Richard Becker, John Chambers, and Allan Wilks.  R programmers don't write big
servers or software systems; instead, they write and modify small data
processing pipelines as a means to facilitate interaction with digital data.
This leads to ``front-line'' R code (i.e., code written for users, not
programmers) not being made available on typical platforms like Github.
\AT{Maybe front-line code isn't a good word, is there a good way to describe
  non-library code?}  Put differently, R is essentially a really big
domain-specific language.

%
\section{The R Programming Language}

@@

\subsection{The \texttt{genthat} Package}

@@

\AT{We use/modify the {\tt genthat} tracer, probably worth going in to more
  detail here.}
%

\section{The Method}

@@

%
%
%
%
\section{Related Work}

\AT{Not sure what the best place for this is, but we should discuss these papers somewhere.}

The idea of measuring polymorphism via some program analysis isn't new.
For instance, some work~\cite{aakerblom2015measuring} ... .

More generally, there is an existing literature on analyzing usage patterns of language features.
For instance, the dynamic features of Smalltalk were analyzed in some work~\cite{callau2011howdevelopers}, ...

Other analysis work~\cite{milojkovic2017duck} ... .
